On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-29 docs/mvfits_paper/mvf.tex
Update Methods::C

\par However, we note that $\hat{P}$'s depending on $g$ signals that there is more to be done.

@@

In particular, let us briefly consider the effect of zero-mean noise on $g$, e.g. $g \rightarrow g+n$.

@@

\par Much as in the case of multivariate polynomial fitting, we are left with an un unknown number and content of basis symbols.

>>>>

\par However, we note that $\hat{P}$ depends on $g$ signals.

@@

Let us briefly consider the effect of zero-mean noise on $g$, e.g. $g \rightarrow g+n$.

@@

\par Much as in the case of multivariate polynomial fitting, we are left with an unknown number and content of basis symbols.
